Hydras and Cie (Draft) \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-20 doc/JFLA2022/paper.tex
minor corrections

\begin{todo}
  Work destined both to Coq-users and people interested in discrete math ?
 \end{todo}

\subsection{Perspectives}

@@

>>>>

%\subsection{Perspectives}

@@

The \emph{Hydra-battles} project is not limited to the study of ordinal numbers and applications, but aims to be an experimental platform for the collaborative development of commented libraries of formal proofs. For instance, we are also developing 
a module about efficient exponentiation algorithms, and hope
to extend our priject to new topics.
